---
title: "esm206_lab7"
author: "Drew Andersen"
date: "11/9/2021"
output: html_document
---

```{r setup, include = TRUE, message = FALSE, warnings = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warnings = FALSE)

library(tidyverse)
library(palmerpenguins)
library(GGally)
library(kableExtra)
library(broom)
library(modelsummary)
library(stargazer)
```

## Explore Penguins
Use `GGally::ggpairs()` to create a pairs plot. 

```{r}
ggpairs(penguins) 
```
kind of overkill --> so let's simplify variables
lets to bill_length through body mass
```{r}
penguins %>% 
  select(species,bill_length_mm:body_mass_g) %>% 
  ggpairs(aes(color = species))
```

##Multiple Linear regression 
We are going to try to understand (a bit better) relationships between multiple predictor variables and an outcome which is penguins body mass.
Diff predictor variables:
-species, flipper length, sex, bill_depth 

##Model 1
Model body mass based on only flipper length and bill depth(bad idea...there are important variables missing)

```{r}
model_1 <- lm(body_mass_g ~ flipper_length_mm + bill_depth_mm, data = penguins)
summary(model_1)
```
Use the R^2 value for multiple linear regression
  - X% of variance in penguin body mass is explained by this model with these two variables 
  
If eerything else is held constant we expect that for every 1 mm increase in flipper length, body mass is expected to increase 51.54g on average. 
