---
title: "esm206_lab7"
author: "Drew Andersen"
date: "11/9/2021"
output: html_document
---

```{r setup, include = TRUE, message = FALSE, warnings = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warnings = FALSE)

library(tidyverse)
library(palmerpenguins)
library(GGally)
library(kableExtra)
library(broom)
library(modelsummary)
library(stargazer)
```

## Explore Penguins
Use `GGally::ggpairs()` to create a pairs plot. 

```{r}
ggpairs(penguins) 
```
kind of overkill --> so let's simplify variables
lets to bill_length through body mass
```{r}
penguins %>% 
  select(species,bill_length_mm:body_mass_g) %>% 
  ggpairs(aes(color = species))
```

##Multiple Linear regression 
We are going to try to understand (a bit better) relationships between multiple predictor variables and an outcome which is penguins body mass.
Diff predictor variables:
-species, flipper length, sex, bill_depth 

##Model 1
Model body mass based on only flipper length and bill depth(bad idea...there are important variables missing)

```{r}
model_1 <- lm(body_mass_g ~ flipper_length_mm + bill_depth_mm, data = penguins)
summary(model_1)
```

Use the R^2 value for multiple linear regression
  - X% of variance in penguin body mass is explained by this model with these two variables 
  
If eerything else is held constant we expect that for every 1 mm increase in flipper length, body mass is expected to increase 51.54g on average. 

Actually -- we think that a model for penguin body mass should contain variables species, flipper length, and pegnuin sex.
```{r}
model_2 <- lm(body_mass_g ~ species + flipper_length_mm + sex, data = penguins)
```

on average we expect a male penguins to be 530 g larger tha a female that is similiar in every other way. 

## Visualize this model
```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point(aes(color = species)) +
  facet_wrap(~sex)
```
## A couple ways to get and report MLR model outcomes
use broom::tidy() to get model coefficients into a tiny data frame 
```{r}
penguin_model2_coef <- tidy(model_2)
penguin_model2_coef

plot(model_2)
```
I am going to pull ou sex coefficient `r penguin_model2_coef$estimate[5]`

## Look at model diagnostics 

Use the plot() function

## report the model outputs in a summary table 

Use modelsummary:
```{r}
modelsummary(model_2)
```
```{r, results = "asis"}
stargazer(model_2, type = "html")
```

